---
title: "Installation Instructions CWS Ontario Shiny App"
author: "David Hope"
format: docx
---


```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(eval=FALSE, echo = T)



```


## Requirements

To install a local version of the app, you'll need to install `R` from the 
software centre.

You'll also need the "pak" package. It can be installed using: 
```{r}
install.packages("pak")
```

## Package installation

Once you have the "pak" package installed, should be able to 
run the following code to install the 'Shiny.CWS.ONT' package:
```{r}
pak::pak(glue::glue("{path_to_shiny_zip}/Shiny.CWS.ONT_0.1.0.zip"))
```
or  you could download the above file to your working directory and run:
```{r}
pak::pak("Shiny.CWS.ONT_0.1.0.zip")
```

## Data import

The R packages comes with a small sample of the data, which will allow you to test out the app. However to
get the app running with the full dataset you'll need to copy the following file to your local computer and unpack in a working directory: 
[Ctrl+Click here to open the Data_Explorer_Shiny folder](`r paste0(path_to_shiny)`)

[2025-02-05_Shiny_Data.7z](`r glue::glue("{path_to_shiny_zip}/Shiny.CWS.ONT_0.1.0.zip")`)


## To run the app:

In order to get the app running run the following code in your R console or Rstudio.


```{r}
library('Shiny.CWS.ONT')
update_data(base_folder_path ="path/to/data/folder/",
            all_events_rds = "all_events.rds",
            all_counts_rds = "counts.rds", 
            project_status_rds = "project_status.rds",
            locations_rds = "locations.rds")

run_shiny_app()
```
Be sure to **replace  "path/to/data/folder/” with the path to your data folder.**
The `update_data()` function will load in the full dataset you downloaded and 
needs to be run every time you load the app or you will just have the example
data loaded.


## Bug report and feature request


If you run into issues you can help improve and maintain the app by letting us know.
This can be done by 
by creating a bug report form at the following folder (Ctrl + Click to open):
[BUG_REPORTS](`r glue::glue("{path_to_shiny_zip}/BUG_REPORTS")`). You will find a template for the bug report there.


If there are specific features you'd like to see in the app you can complete a feature
request here: [FEATURE_REQUESTS](`r glue::glue("{path_to_shiny_zip}/FEATURE_REQUESTS")`). A template is also available here. 

Completed forms can be emailed to [david.hope@ec.gc.ca](mailto:david.hope@ec.gc.ca) or left in the above
folders.












